Psychological Needs During Intergroup Contact

### 2022-01-07 Methods-and-Results.Rmd
shortened General S3

\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps. First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes. Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions). We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes. This is again consistent with the results we found in the first study but inconsitent with the significant relationship we find in the second study.

@@

However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`). Given the missing aggregate relationship between number of interactions and outgroup attitudes, we find no significant effect of interactions themselves nor do we find a significant interaction effect. This result mirrors that of study one but is inconsistent with the second study. But again this inconsistency is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.

@@

We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B). Thus, in our third dataset we find some mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect). However, while the aggregate data is partly inconsistent with the first two studies, the within person contemoranous effect of intergroup contact is consistent across all three studies.

>>>>

@@

@@

\subsubsection{Contact Hypothesis}We again started with a general test of the contact hypothesis, as in Studies 1 and 2. We found no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (\textit{r} < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). However, we did find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). When considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect. This result mirrors that of study one but is inconsistent with the second study. Additionally in a multilevel regression to check for contemporaneous effects within the participants, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B). Thus, in our third data set we again found mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect). However, while the aggregate data is partly inconsistent with the first two studies, the within person contemporaneous effect of intergroup contact is consistent across all three studies.

### 2022-01-07 Methods-and-Results.tex
shortened General S3

We tested the most general contact hypothesis in two steps. First, we
assessed whether more intergroup interactions were related to to more
positive outgroup attitudes. Second, we tested whether a potential
positive effect on outgroup attitudes depended on the interaction
quality (jointly with the number of interactions). We find no
significant correlation between intergroup contact and average outgroup
attitudes --- for neither the total number of outgroup interactions
(\textit{r} = 0.01, \textit{p} = 0.946) and the number of measurement
beeps with an interaction (\textit{r} = 0.13, \textit{p} = 0.291). This
is to say that within our data, participants with more outgroup
interactions did not have significantly more positive or negative
outgroup attitudes. This is again consistent with the results we found
in the first study but inconsitent with the significant relationship we
find in the second study.

However, we do find a significant correlation between the participants'
Average Interaction Quality and their Average Outgroup Attitudes
(\textit{r} = 0.25, \textit{p} = 0.036). Thus, when considering the
number of interactions and average interaction quality jointly in a
linear regression, we only find a main effect of average perceived
interaction quality on predict outgroup attitudes (\textit{b} = 0.36,
\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07). Given
the missing aggregate relationship between number of interactions and
outgroup attitudes, we find no significant effect of interactions
themselves nor do we find a significant interaction effect. This result
mirrors that of study one but is inconsistent with the second study. But
again this inconsistency is not necessarily surprising given that the
variables aggregate all within person variation and there were
substantially more measurements where participants did not have an
interaction (but reported their outgroup attitudes) than measurements
that followed an outgroup contact.

We additionally used a multilevel regression to check whether having an
interaction with an outgroup member had a situational (i.e.,
contemporaneous) effect within the participants. We find that having an
outgroup interaction is indeed associated with significantly more
positive outgroup attitudes within the participants (random slopes
model; \textit{b} = 5.63, \textit{t}(3834) = 6.61, \textit{p}
\textless{} .001, \textit{95\%CI}{[}3.97, 7.29{]}), even after
controlling for having an interaction with a non-Dutch (which did not
relate to outgroup attitudes independently; For full results see Online
Supplementary Materials B). Thus, in our third dataset we find some
mixed results, outgroup contacts are not significantly related to
outgroup attitudes on aggregate between participants and this effect is
also not suppressed by a average interaction quality (i.e., no
interaction effect). However, while the aggregate data is partly
inconsistent with the first two studies, the within person contemoranous
effect of intergroup contact is consistent across all three studies.

>>>>

We again started with a general test of the contact hypothesis, as in
Studies 1 and 2. We found no significant correlation between intergroup
contact and average outgroup attitudes --- for neither the total number
of outgroup interactions nor the number of measurement beeps with an
interaction (\textit{r} \textless{} 0.13, \textit{p} \textgreater{}
0.291). However, we did find a significant correlation between the
participants' Average Interaction Quality and their Average Outgroup
Attitudes (\textit{r} = 0.25, \textit{p} = 0.036). When considering the
number of interactions and average interaction quality jointly in a
linear regression, we only find a main effect of average perceived
interaction quality on predict outgroup attitudes (\textit{b} = 0.36,
\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07) but no
significant effect of the number of contacts nor an interaction effect.
This result mirrors that of study one but is inconsistent with the
second study. Additionally in a multilevel regression to check for
contemporaneous effects within the participants, we found that having an
outgroup interaction was indeed associated with significantly more
positive outgroup attitudes within the participants (random slopes
model; \textit{b} = 5.63, \textit{t}(3834) = 6.61, \textit{p}
\textless{} .001, \textit{95\%CI}{[}3.97, 7.29{]}), even after
controlling for having an interaction with a non-Dutch (which did not
relate to outgroup attitudes independently; For full results see Online
Supplementary Materials B). Thus, in our third data set we again found
mixed results, outgroup contacts are not significantly related to
outgroup attitudes on aggregate between participants and this effect is
also not suppressed by a average interaction quality (i.e., no
interaction effect). However, while the aggregate data is partly
inconsistent with the first two studies, the within person
contemporaneous effect of intergroup contact is consistent across all
three studies.
